\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-05-15 trunk/textos/dsrt/blindengaoi.tex
blinded

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%AQUI OS AUTORES
\author{\IEEEauthorblockN{Carlos Eduardo B. Bezerra,
	Fábio R. Cecin,
	Cláudio F. R. Geyer}
\IEEEauthorblockA{Federal University of Rio Grande do Sul\\
	Bento Gonçalves, 9500, Porto Alegre, RS, Brazil,\\
	Email: \{carlos.bezerra, fcecin, geyer\}@inf.ufrgs.br}}

@@

This work is part of the P2PSE \cite{crippa2007pps} project, which is currently based on a peer-to-peer distribution, but still looking for an ideal model. Hence, we propose here an alternative that consists of a virtual environment partitioned into regions - each managed by a different server - on which the \malg\ algorithm is based. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster (Figure \ref{partitions}).

@@

% use section* for acknowledgement
\section*{Acknowledgment}

The development of this work was supported by the Funding for Studies and Projects (FINEP), a brazilian research agency, through the P2PSE project (P2PSE-5849-1).

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%AQUI OS AUTORES
%\author{\IEEEauthorblockN{Author}
%\IEEEauthorblockA{Institute\\
%	Address,\\
%	Email: \{\_\_\_\_\_\_\_\}@\_\_\_\_\_.\_\_\_}}

@@

This work is based on a virtual environment partitioned into regions, each managed by a different server. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster \mbox{(Figure \ref{partitions})}.

@@

% use section* for acknowledgement
%\section*{Acknowledgment}

%The development of this work was supported by the Funding for Studies and Projects (FINEP), a brazilian research agency, through the P2PSE project (P2PSE-5849-1).
